% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion -- try higher (eg 6.0) if not enough space

%\addtolength{\textwidth}{2cm}
%\addtolength{\hoffset}{-1cm}
%\addtolength{\textheight}{2cm}
\addtolength{\voffset}{-2cm}

\begin{document}

% TODO: Make title look better and try to save some space!
% REMINDER: ctrl+t = comment, ctrl+u = uncomment (in Texmaker)

%% Option A: Name centred followed by a horizontal line. Contact info centred below the line.
% \moveleft.5\hoffset\centerline{\large\bf Dennis Ideler} % Center name over entire width of resume
% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Draw line the width of resume
% \moveleft.5\hoffset\centerline{214 Pelham Road}
% \moveleft.5\hoffset\centerline{St. Catharines, Ontario L2S 1W9}
% \moveleft.5\hoffset\centerline{289-697-1010}
% \moveleft.5\hoffset\centerline{dennisideler.com}
% \moveleft.5\hoffset\centerline{ideler.dennis@gmail.com}

%% Option B: Name and contact info on the same line, with a horizontal line below.
% \moveleft1\hoffset\hbox{\large{\bf{DENNIS IDELER}} $\bullet$ St. Catharines, ON L2S 1W9 $\bullet$
%  289-697-1010 $\bullet$ di07ty@brocku.ca} % Use ideler.dennis@gmail.com when I graduate?
% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

% Option C: Name with horizontal line below. Contact info right below and on the same line.
% \moveleft1\hoffset\hbox{\large{\bf{DENNIS IDELER}}} % Use this one for a left-justified name.
 \moveleft.5\hoffset\centerline{\large\bf DENNIS IDELER} % This name option is centred.
% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
 \moveleft.5\hoffset\centerline{23 Woodcrest Dr, St. Catharines, ON L2T 2Y2 $\bullet$
 289-697-1010 $\bullet$ di07ty@brocku.ca $\bullet$ www.dennisideler.com}
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

%% Option D: Name with horizontal line, and CONTACT INFO section below.
% \moveleft.5\hoffset\centerline{\large\bf Dennis Ideler} % Center name over entire width of resume
% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Draw line the width of resume

\begin{resume}

%\section{CONTACT INFO} % This belongs to title option D
%  {\sl Address:} 214 Pelham Rd, St. Catharines, Ontario L2S 1W9 \\
%  {\sl Phone:} 289-697-1010 \\
%  {\sl Website:} dennisideler.com \\
%  {\sl Email:} ideler.dennis@gmail.com

% Use an objective when looking for a permanent or specific position.
% E.g. See my LinkedIn objective.

%\section{OBJECTIVE}  A position in the field of computers with special 
%                interests in business applications programming, 
%                information processing, and management systems. 

% TODO: bold appropriate sections
% TODO: move education lower or keep at the top?
% TODO: move dates to the LHS?
\section{EDUCATION}
  {\sl Bachelor of Science (B.Sc.),} Computer Science (Honours \& Co-op) \\
  % \sl will be bold italic in New Century Schoolbook
	% (or any postscript font) and just slanted in Computer Modern (default) font
  Concentration in Intelligent Systems \\
  Brock University, St. Catharines, Ontario, 
  \hfill Sep 2007 - Present \\
  % TODO: itemized list with school accomplishments?
                
  {\sl Voorbereidend Wetenschappelijk Onderwijs (VWO),} Natuur en Techniek \\
  or {\sl Pre-university Secondary Education,} Nature and Technology \\
  Milton Peters College, St. Maarten, Netherlands Antilles, 
  \hfill Aug 2001 - Jun 2007 \\
	% TODO: itemized list with school accomplishments?

% TODO: Create categories (Beginner, Intermediate, Advanced, Proficient, Fluent)?

\section{TECHNICAL \\ SKILLS}
	\begin{tabular}{l l}
	{\sl \textbf{Software Development:}} &
  C++, C, Java, Prolog, Python, \\ (in order of proficiency) &
  Linux Shell Scripting, Ruby, LC-3 Assembler \\

	{\sl \textbf{Web Development:}} &
	HTML, CSS, JavaScript \\

	{\sl \textbf{Mobile Development:}} &
	Windows Phone 7 \\

	{\sl \textbf{Source Control:}} &
	Git, Subversion (SVN), GitHub, Google Code \\

	{\sl \textbf{API's/Libraries:}} &
	OpenGL, jQuery \\

	{\sl \textbf{Technical Writing:}} &
	\LaTeX, UML, Markdown, reStructuredText \\

	{\sl \textbf{Business Collaboration Software:}} &
  MS SharePoint, IRC, Trac, phpBB3 \\
	  
	{\sl \textbf{Database:}} &	  
  SQL \\	  
	  
	{\sl \textbf{Operating Systems:}} &
  GNU/Linux, MS Windows (XP/Vista/7)

	\end{tabular}	 

\section{EXPERIENCE}
% STAR: Situation, Task, Action, Result
% BAR: Background, Action, Result

	\textbf{Free and Open Source Software Learning Centre} \hfill Sept - Dec 2011 \\
    {\sl Technical Writer for Freeseer project} \hfill % freeseer.github.com
	\begin{itemize}  \itemsep -2pt % Reduce space between items.
	  \item First Brock student to participate in the Undergraduate Capstone Open Source Projects
	  (UCOSP) program. My case is being used to attract other students.
	  \item Used agile and open source processes in a distributed development environment.
	  \item Localized Freeseer to Dutch by translating the software interface and messages.
	  \item Designed and built a home page for the project using HTML5 standards.
    \item Wrote a new simplified README with focus on readability and content.
	  \item Wrote a Wikipedia article for Freeseer from a neutral perspective.
	  \item Wrote comprehensive user and contributor documentation using Sphinx.
	  \item Collaborated as a team player while posting and updating issues,
	  communicating via IRC, mailing list, video conferencing, and blog posts.
	  \item Frequently presented new ideas, suggestions, feedback, and constructive criticism to the team.
	\end{itemize}

	\textbf{Ministry of Transportation of Ontario} \hfill May - Dec 2010 \\
    {\sl Systems Analyst (Co-op Student)} \hfill St. Catharines, Ontario % & Information Architect
	\begin{itemize}  \itemsep -2pt % Reduce space between items.
	  \item Team member of the Business Support, Policy \& Planning Unit.
	  Responsible for assisting clients in the ministry with consultation, technical support,
	  and software solutions.
	  \item Worked with supervisors, co-workers and consultants to architect, fabricate,
	  and maintain a new ministry-wide Intranet which utilized SharePoint 2007.
	  \item Responsible for updating the Major Applications Portfolio Strategy (MAPS) database.
	  Interviewed several project managers in a timely fashion to extract information from 30+
	  projects. Project information is used for risk assessment.
	  \item Refactored an embedded security request form that was used throughout the
	  Ontario Public Sector to request new keycards. Improved performance and design,
	  implemented new features, and fixed bugs. Wrote approximately 1000 lines of negative code
	  by removing redundancies \& using more concise constructs.
	  \item Collaborated with business architects on the Training Management System project
	  to produce class diagrams, system context diagrams, system use case models,
	  an access control matrix, and a GUI design specification guide.
	\end{itemize}

% LinkedIn
% ===========
% Business Support, Policy & Planning Unit (BSPPU) is a unit in the Labour & Transportation Cluster.
%
%Projects I contributed to include (but not limited to):
%• MTO Intranet Migration Project (IMP)
%• Training Management System (TMS)
%• Major Applications Portfolio Strategy (MAPS)
%• eLearning Project
%• Security eForm
%• Green IT Initiative

% G Docs
% =======
% https://docs.google.com/document/d/1SYv0lMJ08cerV27jlB9FtcZMBzTrjjNJKbDexYbnge0/edit?hl=en_US

	\textbf{Maestro Media Center} \hfill Sep 2009 - Apr 2010 \\
    {\sl Deputy Leader} \hfill St. Catharines, Ontario
	\begin{itemize}  \itemsep -2pt % Reduce space between items.
	  \item Demonstrated strong leadership skills as the deputy leader of a 7-person team for a $3^{rd}$
	  year Software Engineering course at Brock University.
	  \item Used agile software development methodologies to create a fully functional, cross-platform,
	  media center. See code.google.com/p/brockbots
	  \item Utilized strong communication and listening skills when dealing with the client
	  (our professor) and teammates on a weekly basis via meetings and emails.
	  \item Demonstrated the ability to work effectively in a team and set and achieve realistic
	  goals by organizing, planning, and executing tasks and meeting deliverables on schedule.
	  \item Maintained a positive attitude during minor project failures and encouraged teammates
	  rather than discouraging them. For example, influenced teammates to use pair programming
	  when they were having difficulty with some coding tasks, which resulted in quicker
	  completion, more team communication, and an overall better understanding of the project for
	  those involved.
	  \item Received an outstanding peer review and successfully delivered a project on time with my team.
	  Our team produced the highest graded project that year.
	\end{itemize}

	\textbf{GenieKnows Inc.} \hfill Jan - Apr 2009 \\
    {\sl Data Specialist (Co-op Student)} \hfill Halifax, Nova Scotia
	\begin{itemize}  \itemsep -2pt % Reduce space between items.
	  \item Enhanced business data for results used to provide the search and mapping features of
	  GenieKnows Local Search (now yellowee.com).
	  Responsible for collection of data from various sources through Automated Data Collection.
	  \item Daily duties included: identifying data requirements,
	  researching data sources, automating the downloading and processing/formatting of data,
	  evaluating data quality, writing technical documentation, logging bugs, and logging progress.
	  \item Simulated user activity to overcome the ``ghost town'' effect shortly after user
	  profiles and business reviews were introduced. % TODO: keep or remove?
	  \item Researched methods and implementations of specialized crawling and presented findings
	  to R\&D team.
	  Utilized knowledge to develop specialized web crawlers for pages on the Surface Web and Deep Web.
	  \item Collaborated in teams to present creative ideas during research meetings and company-wide
	  brainstorming activities.
	\end{itemize}

	\textbf{Antek: IT Solutions \& Software} \hfill Jun - Sep 2008 \\
    {\sl Computer Technician (Holiday Worker)} \hfill Sint Maarten, Caribbean
	\begin{itemize}  \itemsep -2pt % Reduce space between items.
	  \item Utilized creative problem solving skills and an analytic approach to set up, diagnose,
	  and repair computers, hardware, software, and networks.
	  \item Assisted clients with friendly customer service and technical support.
	  \item Quickly adapted to different work environments and situations when executing tasks at
	  diverse organizations and working in a team or individually.
	\end{itemize}

\vfill

\section{HONOURS \\ AND AWARDS}

  \textbf{Dean's Honour List} \hfill 2011 \\
    {\sl Brock University, Faculty of Mathematics and Science}

  \textbf{Best Elected Residence Action Council Member} \hfill 2008 \\
    {\sl Brock University, Quarry View Residence}

  \textbf{Government of Sint Maarten Study Financing Grant} \hfill 2007 - Present \\
    {\sl Ministry of Education, Island of Saint Martin}
 
\section{COMPETITIONS}

  \textbf{ACM-ICPC East Central North America} \hfill Oct 2008, 2009, 2010, 2011 \\
    {\sl International Collegiate Programming Contest} \\
    {\sl McMaster University, University of Windsor} % TODO: consider removing this line (save space).

  \textbf{Great Canadian Appathon} \hfill Mar 2011 \\
    {\sl Team placed in top 25 of the national competition} \\
    {\sl University of Waterloo hub}

  \textbf{Computer Science Games} \hfill Mar 2010, 2011 \\
    {\sl Team placed in top 10} \\
    {\sl Polytechnique de Montreal, Concordia University}

%  \textbf{GameBattles: Halo 2} \hfill Summer 2007 \\
%    {\sl Team placed 1st in the Halo 2 4v4 online ladder} \\
%    {\sl GameBattles.com}

  \textbf{Mathematics A-lympiad Preliminaries} \hfill Mar 2006 \\
    {\sl Team placed 2nd in the regional qualifier} \\
    {\sl Milton Peters College, Sint Maarten}

  \textbf{St. Maarten Science Fair} \hfill Apr 2005 \\
    {\sl Presented a solution to an enormous traffic congestion problem} \\
    {\sl Milton Peters College, Sint Maarten}

%\section{TECHNICAL PROJECTS}
%  TODO

\section{EXTRA-CURRICULAR \\ INVOLVEMENT}

  \textbf{Judge for Niagara Secondary Schools Programming Contest} \hfill May '11 - '12 \\
    {\sl Computer Science Department, Brock University}

  \textbf{Volunteer at Computer Science Fair for CSEdWeek} \hfill Dec 2011 \\
    {\sl Computer Science Department, Brock University}

  \textbf{Guest speaker at Co-op Student Panel Workshop} \hfill Oct 2010 \\
    {\sl Co-op Office, Brock University}

  \textbf{President and Founder of Brock Chess Club} \hfill Jan - Apr 2010 \\
    {\sl Math Help Centre, Brock University}

  \textbf{Brock CS Recruiter at Ontario Universities' Fair} \hfill Sep 2009 \\
    {\sl Metro Toronto Convention Centre, Toronto}

  \textbf{Executive of Brock Computer Science Club} \hfill Sep 2009 - Present \\
    {\sl Brock Chapter of the ACM, Brock University (See brockcsc.ca)}

%  \textbf{Volunteer at Co-op Orientation} \hfill Sep 2009 \\
%    {\sl Co-op Office, Brock University}

  \textbf{Co-founder and Administrator of BrockBots} \hfill Mar 2009 - Sep 2010 \\
    {\sl Formerly a CS messageboard at www.brockbots.cosc.brocku.ca}
    
%  \textbf{Member of Computer Science Club} \hfill Sep 2007 - Present \\
%    {\sl Brock Chapter of the ACM, Brock University}

  \textbf{Elected Residence Action Council Member} \hfill Sep 2007 - Apr 2008 \\
    {\sl Quarry View Residence, Brock University}
 
%\section{ADDITIONAL} % \\QUALIFICATIONS}
%  \begin{itemize}
%    \item Bilingual (English \& Dutch)
%    \item Comfortable being a de-facto team leader across disciplines
%    \item Keen eye for detail and elegant user interface design
%  \end{itemize}

% Don't include 'References available upon request'. That's obvious and a waste of space.
\end{resume}
\end{document}