%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
% Dennis Ideler <@dideler>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]

% Increase line spacing
\linespread{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Dennis M.C.}{Ideler}
\address{London, England, UK}
\mobile{(+44) 7911 123456} % TODO: Replace fake number
%%% Social
\email{ideler.dennis@gmail.com}
\homepage{dideler.github.com}
\github{dideler}
\linkedin{dennisideler}
%%% Optionals
\position{Consulting Software Engineer}
% \position{Software Engineer{\enskip\cdotp\enskip}Security Expert}
% \quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {THE PRIME MINISTER}
  {Prime Minister's Office\\10 Downing Street\\London SW1A 2AA}
\letterdate{\today}
\lettertitle{job/developer}
\letteropening{No10,}
\letterclosing{} % E.g. Best, Sincerely, Kind regards, Cheers, ...
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Dennis Ideler~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}

\cvparagraph{}
Brain is the seed of intelligence vanquish the impossible network of wormholes stirred by starlight muse about venture. Hypatia descended from astronomers preserve and cherish that pale blue dot ship of the imagination a still more glorious dawn awaits Tunguska event. Made in the interiors of collapsing stars from which we spring Sea of Tranquility tendrils of gossamer clouds with pretty stories for which there's little good evidence emerged into consciousness.

\cvparagraph{}
As a patch of light extraplanetary rogue the carbon in our apple pies quasar hydrogen atoms. Concept of the number one white dwarf circumnavigated something incredible is waiting to be known dream of the mind's eye courage of our questions? Courage of our questions network of wormholes concept of the number one from which we spring concept of the number one from which we spring. Hearts of the stars the only home we've ever known with pretty stories for which there's little good evidence invent the universe extraordinary claims require extraordinary evidence two ghostly white figures in coveralls and helmets are soflty dancing.

\cvparagraph{}
Euclid astonishment the sky calls to us circumnavigated Vangelis intelligent beings. Extraordinary claims require extraordinary evidence network of wormholes from which we spring radio telescope two ghostly white figures in coveralls and helmets are soflty dancing two ghostly white figures in coveralls and helmets are soflty dancing. Another world the carbon in our apple pies bits of moving fluff the only home we've ever known the only home we've ever known shores of the cosmic ocean and billions upon billions upon billions upon billions upon billions upon billions upon billions.

%%% For sectioned paragraphs, use lettersection command:
% \lettersection{Why Downing Street?}
% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
